A survey of HTTP caching options on the open Semantic Web

### 2015-01-19 sanity/paper1.tex
Trim pass
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1011 43ef1190-90fd-4dd7-a769-d0121f02b80e

The implications of HTTP for query caches has been discussed by
\cite{kaseicache}, where it is shown how changes can be tracked
efficiently using different data structures. In \cite{sparqlproxy} the
authors implemented a reverse proxy that controlled the changes to the
dataset, and therefore could make sure the proxy had all the
information needed to determine freshness. We are interested in the
situation where the changes cannot be controlled.

@@

We next consider the simple heuristic freshness lifetime as suggested
RFC7234, Section~4.2.2 and detailed in the introduction.

>>>>

In \cite{sparqlproxy} the authors implemented a reverse proxy that
controlled the changes to the dataset, and therefore could make sure
the proxy had all the information needed to determine freshness. We
are interested in the situation where the changes cannot be
controlled.

@@

We next consider the simple heuristic freshness lifetime as suggested
RFC7234, Section~4.2.2 and mentioned in the introduction.
